---
title: "Stat 3302 Report"
author: "Group H: Sam Lefebvre.22, Nina Wei.1241, Maggie Miller.10302, Kevin Song.1649"
date: "4/20/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

## Methods

First, we import the two datasets needed for the two studies.
```{r}
study1 = read.csv("Study1Data.csv")
study2 = read.csv("Study2Data.csv")
```

### Study 1

Study 1 has two binary logistic regression models, Model 1 and Model 2.

#### Model 1
```{r}
s1mod1 = glm(sent ~ trust, family=binomial, data=study1)
b = coef(s1mod1)
names(b) = c("Intercept", "Trustworthiness")
odds.ratio = exp(b)
s1mod1.df = as.data.frame(cbind(b, odds.ratio))
```

#### Model 2
```{r}
s1mod2 = glm(sent ~ trust + zAfro + attract + maturity + zfWHR + glasses + tattoos, family=binomial, data=study1)
b = coef(s1mod2)
names(b) = c("Intercept", "Trustworthiness", "Afrocentricity", "Attractiveness", "Facial maturity", "Facial width-to-height ratio", "Presence of glasses", "Presence of tattoos")
odds.ratio = exp(b)
s1mod2.df = as.data.frame(cbind(b, odds.ratio))
```

### Study 2

Study 2 has two binary logistic regression models, Model 1 and Model 2.

#### Model 1
```{r}
s2mod1 = glm(sent ~ trust, family=binomial, data=study2)
b = coef(s2mod1)
names(b) = c("Intercept", "Trustworthiness")
odds.ratio = exp(b)
s2mod1.df = as.data.frame(cbind(b, odds.ratio))
```

#### Model 2
```{r}
s2mod2 = glm(sent ~ trust + zAfro + attract + maturity + glasses + served, family=binomial, data=study2)
b = coef(s2mod2)
names(b) = c("Intercept", "Trustworthiness", "Afrocentricity", "Attractiveness", "Facial maturity", "Presence of glasses", "Time served")
odds.ratio = exp(b)
s2mod2.df = as.data.frame(cbind(b, odds.ratio))
```
## Results

### Study 1

For Study 1, we were able to reproduce the two binary logistic regression models presented in the table.

#### Model 1
```{r}
summary(s1mod1)
kable(s1mod1.df)
```

#### Model 2
```{r}
summary(s1mod2)
kable(s1mod2.df)
```

### Study 2

For Study 2, we were able to reproduce the two binary logistic regression models presented in the table. For Model 1, the summary table in the paper displayed the odds ratio of `Trustworthiness` as 0.56 when it was actually 0.21 stated in another paragraph. We obtained an odds ratio of 0.21 for `Trustworthiness` in our reproduction of Model 1.

#### Model 1
```{r}
summary(s2mod1)
kable(s2mod1.df)
```

#### Model 2
```{r}
summary(s2mod2)
kable(s2mod2.df)
```

