---
title: "Stat 3302 Report"
author: "Group H: Sam Lefebvre.22, Nina Wei.1241, Maggie Miller.10302, Kevin Song.1649"
date: "4/20/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

## Methods

There was one primary methodology to analyze the relationship between facial trustworthiness and actual criminal sentences across two studies. Both studies involved the gathering of faces of convicted murderers who had been sentenced to either death or life in prison.

### Study 1

In Study 1, the facial trustworthiness of every death-row inmate in Florida was analyzed in order to investigate the relationship between facial trustworthiness and sentencing among real criminals serving life sentences or awaiting execution. Stimulus selection was utilized as 376 white and black males were selected, excluding female inmates and inmates of other races. This was done in order to keep sex and race uniform. A control group of inmates sentenced to life imprisonment was selected to compare against death row inmates.

Next, in order to collect data on the facial traits of the inmates, defendants were divided into seven sets, each set containing equal life sentences and death row sentences, as well as racial splits. They obtained trustworthiness ratings by asking 208 American workers from Amazon Mechanical Turk to rate their trustworthiness from 1 to 8. Ratings of other facial traits were collected, indluding Afrocentricity, attractiveness, facial maturity, glasses, and tattoos. These trustworthiness ratings were compared to a fWHR rating (aggression rating) using ImageJ, and there was a small negative correlation between them, suggesting an independent relationship.

A logistic regression model was used in order to determine the relationship of facial trustworthiness and predicted sentencing outcomes. The sentence outcome (0 = life, 1 = death) was regressed onto trustworthiness of a binary logistic regression model, as well as the covariates (Afrocentricity, attractiveness, facial maturity, fWHR, glasses, tattoos).


### Study 2

Study 2 tested the relationship between perceived trustworthiness and criminal sentencing among innocent individuals. Stimulus selection was utilized to select from a group of 107 people. They recorded information such as the sentence received, length of time served, crime committed, year of conviction, and state the conviction occurred. They eliminated people who lived in a state without a death sentence, and selected people whose crimes would have made them eligible for the death sentence. This resulted in a total of 37 people, 20 of whom sentenced to life and 17 to death.

American workers from the Amazon Mechanical Turk were again asked to rate each of the 37 people for trustworthiness, Afrocentricity, attractiveness, and facial maturity. These were the same scales as Study 1. Presence of glasses and tattoos were coded for but fWHR (aggression) was unable to be recorded because targets were not uniformly facing the camera.

A logistic regression model was used in order to determine if facial trustworthiness predicted sentencing outcomes for innocent individuals. The sentence outcome (0 = life, 1 = death) was regressed on trust-worthiness of a binary logistic regression model. The outcomes covaried Afrocentricity, attractiveness, facial maturity, the presence of glasses, and the number of years each person served in prison.

## Results

First, we import the two datasets needed for the two studies. `study1` is the dataset used for Study 1, and `study2` is the dataset used for Study 2.
```{r}
study1 = read.csv("Study1Data.csv")
study2 = read.csv("Study2Data.csv")
```

### Study 1

Study 1 has two binary logistic regression models, Model 1 and Model 2. We were able to reproduce the Model 1 and Model 2 presented in Table 1 in the paper.

#### Model 1
```{r}
s1mod1 = glm(sent ~ trust, family=binomial, data=study1)
summary(s1mod1)
b = coef(s1mod1)
names(b) = c("Intercept", "Trustworthiness")
odds.ratio = exp(b)
s1mod1.df = as.data.frame(cbind(b, odds.ratio))
kable(s1mod1.df)
```

#### Model 2
```{r}
s1mod2 = glm(sent ~ trust + zAfro + attract + maturity + zfWHR + glasses + tattoos, family=binomial, data=study1)
summary(s1mod2)
b = coef(s1mod2)
names(b) = c("Intercept", "Trustworthiness", "Afrocentricity", "Attractiveness", "Facial maturity", "Facial width-to-height ratio", "Presence of glasses", "Presence of tattoos")
odds.ratio = exp(b)
s1mod2.df = as.data.frame(cbind(b, odds.ratio))
kable(s1mod2.df)
```

### Study 2

Study 2 has two binary logistic regression models, Model 1 and Model 2. We were able to reproduce Model 1 and Model 2 presented in Table 2 in the paper. For Model 1, the summary table in the paper displayed the odds ratio of `Trustworthiness` as 0.56 when it was actually 0.21 stated in another paragraph. We obtained an odds ratio of 0.21 for `Trustworthiness` in our reproduction of Model 1.

#### Model 1
```{r}
s2mod1 = glm(sent ~ trust, family=binomial, data=study2)
summary(s2mod1)
b = coef(s2mod1)
names(b) = c("Intercept", "Trustworthiness")
odds.ratio = exp(b)
s2mod1.df = as.data.frame(cbind(b, odds.ratio))
kable(s2mod1.df)
```

#### Model 2
```{r}
s2mod2 = glm(sent ~ trust + zAfro + attract + maturity + glasses + served, family=binomial, data=study2)
summary(s2mod2)
b = coef(s2mod2)
names(b) = c("Intercept", "Trustworthiness", "Afrocentricity", "Attractiveness", "Facial maturity", "Presence of glasses", "Time served")
odds.ratio = exp(b)
s2mod2.df = as.data.frame(cbind(b, odds.ratio))
kable(s2mod2.df)
```
